Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
update function

# Read and prepare data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

general_var %>% kable()
```

@@

```{r}
xxx <- function(df, mivariable, mygroup){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest
  # mygroup: factor variable

  # Model formulation
  myformula <- as.formula(paste0(mivariable, " ~ ", mygroup))

@@

  # Multiple comparison 
  tuk <- glht(mymodel, linfct = mcp(mygroup = "Tukey"))

@@

  mymodel
  tm
  aux_name
  mymult
}

 args <- list("Tukey")
           names(args) <- X
           cmp <- do.call(mcp, args)
           glht(fm1, linfct = cmp)

df <- topo
mivariable <- 'slope'
mygroup <- 'site'

ala <- xxx(df=topo, mivariable='slope', mygroup='site' )

@@

# Get table 
mymult <- as.data.frame(table_glht(tuk))
a <- pander(mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
       emphasize.strong.cells = 
               which(mymult < 0.05 & mymult == mymult[,4], arr.ind = T))

>>>>

# Read and prepare data 
```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

general_var %>% kable
```

@@

```{r}
compara <- function(df, mivariable){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest

  output <- list()

  # Model formulation
  myformula <- as.formula(paste0(mivariable, " ~ site"))

@@

  # Multiple comparison 
  tuk <- glht(mymodel, linfct = mcp(site = "Tukey"))

@@

  output$mymodel <- mymodel
  output$tm <- tm
  output$aux_name <- df_letter
  output$mymult <- mymult

  return(output)
}  
```

```{r}

# Select only variables to compare 
compe_sel <- compe %>% dplyr::select(ba:dnn,site)
# Get vector with variables 
variables <- compe %>% dplyr::select(ba:dnn) %>% names()

for (i in variables){

  # apply comparison
  out_compara <- compara(df=compe_sel, mivariable = i)

  out_name  <- paste0('aov_', i)
  assign(out_name, out_compara)

  }

ala <- xxx(df=topo, mivariable='slope')

@@

# Get table 
mymult <- as.data.frame(table_glht(tuk))

for (i in variables){

  mymult <-

  aux <- 
pander(aov_dnn$mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
     emphasize.strong.cells = 
             which(aov_ba$mymult < 0.05 & aov_ba$mymult == aov_ba$mymult[,4], arr.ind = T))

aov_ba$mymult
